Physics-Informed Neural ODEs (PINODE)

### 2023-05-11 presentation/phd_defense_pres.tex
Create slides for ROM introduction; rename slides according to new schematics

\section{Reduced-Order Models}
\subsection{Intro to Reduced-Order Models (ROMs)}

\begin{frame}{Reduced-Order Models}

Schematics, terminology, notation

@@

\begin{frame}{Variations of ROMs}
	Linear, nonlinear, citations
\end{frame}

\begin{frame}{Physics-Informed Loss}
Definition of Physics-informed ML.

Derivation of PI loss through chain rule.

Problem with evaluating RHS of differential equations.

Interpretation with cross-borrowing strength. 
\end{frame}

\begin{frame}{Physics-Informed Koopman Networks}
	Linear latent dynamics

	Paper

	Not a rom so not suitable for downstream tasks. 
\end{frame}

\begin{frame}{Physics-Informed Neural ODEs (PINODE)}
	Nonlinearity in latent space
	- require a lot of data
	- picky to initialization
	- good interpolation bad extrapolation	
\end{frame}

\begin{frame}{PINODE Results on Burgers}
	Add PI loss => Fixes most of the issues
	(example with Burgers)
	Points learned
	- Inform the model about unseen conditions
	Paper reference
\end{frame}

\begin{frame}{PINODE Active}
	> PIKN: "we use it and it works"
	> PINODE: "this is how you need to use it right"
	> PINODE-Active: can we use it right automatically?

	Loop scheme
\end{frame}

\begin{frame}{PINODE Active Results}
	Best result (Burgers)
\end{frame}

\begin{frame}{PINODE-CS}
	Application of the above 
	Loss and setup
\end{frame}

\begin{frame}{PINODE-CS Results}
	Results on Burgers
	Maybe results on a harder problem
\end{frame}

>>>>

\section{PINODE}

\subsection{Intro to Physics-Informed Reduced-Order Models (ROMs)}

\begin{frame}{Data-Driven Modeling of Physical Systems}

1) People used to model physical systems with first-principle knowledge
2) Data-Driven modelling of dynamical systems became a big thing  
3) However, it requires a lot of data 
4) Incorporating prior knowledge is a big recent trend, so history does a spiral

@@

\begin{frame}{Incorporating Knowledge into Models}
1) There are multiple ways of incorporating knowledge into system 
4) The overall umbrella term for it is physics-informed machine learning
2) Some use the equations that model phenomena
3) Some take aspects of it, e.g. symmetries and preservation laws, and forces
A network to respect those
5) Our work falls into the first category of approaches
\end{frame}

\begin{frame}{Reduced-Order Models (ROMs)}
\includegraphics[width=\textwidth]{Figures/roms_1}
\end{frame}

\begin{frame}{Reduced-Order Models (ROMs)}
\includegraphics[width=\textwidth]{Figures/roms_2}
\end{frame}

\begin{frame}{Reduced-Order Models (ROMs)}
\includegraphics[width=\textwidth]{Figures/roms_3}
\end{frame}

\begin{frame}{Reduced-Order Models (ROMs)}
\includegraphics[width=\textwidth]{Figures/roms_4}
\end{frame}

\begin{frame}{Physics-Informed Loss}
1) We introduce physics to this system by adding a term which regularises latent gradient field. 
2) In particular, it forces it to be equal to what a true physics should be under such projection.
3) We can not evaluate physics everywhere but we can at particular carefully-selected points. We call these points collocation points.
4) We feed a lot of collocation points and ask a network to do interpolation \end{frame}

\begin{frame}{Results: Extrapolation to Unknown Regimes}
1) We show that network can indeed interpolate between collocations. Moreover, it can fill the whole unknown regimes of behaviour. (Duffing example with explanation)
\end{frame}

\begin{frame}{Results: Stable Long-Term Predictions}
Fig 3.3.7
\end{frame}

\begin{frame}{Results: Learning From Collocations}
1) Finally we show that collocations can be even more useful than the data itself.
2) The difference is especially prominent in low-data regime.
3) It shows that collocations are powerful source of information and that the network can indeed interpolate between them.
\end{frame}

\begin{frame}{Single-Pixel Imaging}
1) Now we switch gears to show you an application to single-pixel imaging
2) It shows how powerful these differentiable reduced-order models can be in applications besides forecasting and motivate the need to improve those.
3) SPI setup is a single-pixel camera with mirror array… 
\end{frame}

\begin{frame}{Compressive Sensing with Reduced-Order Models}
	1) We introduce a ROM as a relaxation of a PDE-constrained compressive sensing.
	2) We search in the latent space of a ROM for the right trajectory that matches both the ROMs predictions and the compressive-sensing observations
\end{frame}

\begin{frame}{Results: Burger's Equation}
	Results on Burgers
	Maybe results on a harder problem
\end{frame}

\begin{frame}{Results: Kolmogorov Flow OR Real Example}

\begin{frame}{Conclusion}
	Results on Burgers
	Maybe results on a harder problem
\end{frame}
